% LaTeX resume using res.cls
\documentclass{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font  
\usepackage{hanging}
%\usepackage[colorlinks=true,urlcolor=black,citecolor=black,linkcolor=black]{hyperref}
\usepackage[utf8]{inputenc}
\usepackage{color}
\usepackage{hyperref}
%\usepackage{bookmark}
\definecolor{darkblue}{rgb}{0.0,0.0,0.3}
\hypersetup{colorlinks,breaklinks,
	linkcolor=darkblue,urlcolor=darkblue,
	anchorcolor=darkblue,citecolor=darkblue}

%\usepackage{bookmark}

\setlength{\topmargin}{-0.6in}  % Start text higher on the page 
\setlength{\textheight}{9.8in}  % increase textheight to fit more on a page
\setlength{\headsep}{0.2in}     % space between header and text
\setlength{\headheight}{12pt}   % make room for header
\usepackage{fancyhdr}  % use fancyhdr package to get 2-line header
\renewcommand{\headrulewidth}{0pt} % suppress line drawn by default by fancyhdr
\lhead{\hspace*{-\sectionwidth}Alejandro Buren CV} % force lhead all the way left
\rhead{P\'agina \thepage}  % put page number at right
\cfoot{}  % the footer is empty
%\frenchspacing
\pagestyle{fancy} % set pagestyle for the document

% avoid word hyphenation at end of lines
\tolerance=1
\emergencystretch=\maxdimen
\hyphenpenalty=10000
\hbadness=10000

\begin{document} 
\thispagestyle{empty} % this page does not have a header
\name{Dr. Alejandro Daniel Buren}
%\address{222 South Main Street\\
%\address{\href{mailto:aburen@mun.ca}{aburen@mun.ca}\\
%\url{https://www.researchgate.net/profile/Alejandro_Buren}}



	
\address{ 
	\centerline{\href{mailto:aburen@mun.ca}{aburen@mun.ca}}\\
	\centerline{\url{https://www.researchgate.net/profile/Alejandro_Buren}}\\
	\centerline{\url{https://publons.com/researcher/1266176/alejandro-buren}}
%}	
%	Senior Fisheries Biologist\\
%	Ecofish Research Ltd.\\
%	\\	
%	Research Scientist\\
%Fisheries and Oceans Canada
%}
%(709) 772 - 4049\\
%alejandro.buren@dfo-mpo.gc.ca\\
%https://www.researchgate.net/profile/Alejandro\_Buren
}


\begin{resume}
%\vspace{0.1in}
\moveleft.5\sectionwidth\centerline{ }  


\section{EDUCACI\'ON}
\vspace{0.1in} 
 
\textbf{Doctor of Philosophy}. 2015 \\
Memorial University \\
Cognitive and Behavioural Ecology \\
Supervisor: William Montevecchi, Co-Supervisor: Mariano Koen-Alonso.
%\textit{Thesis title}: “The roles of capelin, climate, harp seals and fisheries in the failure of 2J3KL (northern) cod to recover”

\textbf{Master of Sciences}. 2007 \\
Memorial University \\
Cognitive and Behavioural Ecology \\
Supervisor: William Montevecchi, Co-Supervisor: Mariano Koen-Alonso.
%\textit{Thesis title}: ‘Modeling the link between prey availability and diet: common murre and capelin interaction during the breeding season’.

\textbf{Licenciado en ciencias biol\'ogicas}. 2004\\
Universidad Nacional de la Patagonia San Juan Bosco.\\
Supervisor: Enrique Crespo, Co-Supervisor: Mariano Koen-Alonso.
%\textit{Thesis title}: ‘Diet of the beaked skate, \textit{Dipturus chilensis}, off Patagonia during 2000-2001’



\section{EXPERIENCIA PROFESIONAL}
\vspace{0.1in}
%	\subsection{Professional, Research, and Teaching}
\textbf{Bi\'ologo Pesquero Superior,} Ecofish Research Ltd. Sep 2018-presente. T\'{i}tulo en ingl\'{e}s: Senior Fisheries Biologist
	
\textbf{Investigador Adjunto,} Ministerios de Pesquer\'ias y Oc\'eanos, Canad\'a.  2016-Sep 2018. T\'{i}tulo en ingl\'es: Research scientist (SE-RES-02). Fisheries and Oceans Canada (actualmente con licencia sin goce de sueldo)

\textbf{Jefe de Secci\'on Interino,} Ministerios de Pesquer\'ias y Oc\'eanos, Canad\'a. 2013-2018\\ Ocup\'e el cargo de Jefe de Secci\'on de Mam\'iferos Marinos regularmente cuando el titular se encontraba de viaje.

\textbf{Bi\'ologo Pesquero,} Ministerios de Pesquer\'ias y Oc\'eanos, Canad\'a. 2013-2016. T\'{i}tulo en ingl\'es: Aquatic sciences biologist, Fisheries and Oceans Canada.

\textbf{Jefe de C\'atedra,} Memorial University, Departmento de Biolog\'ia. 2012 \\ M\'etodos Cuantitavos en Biolog\'ia.  

\textbf{Facilitador de worskshops del lenguaje R,} Ministerios de Pesquer\'ias y Oc\'eanos, Canad\'a. 2012.

\textbf{Analista de datos,}  Ministerios de Pesquer\'ias y Oc\'eanos, Canad\'a. 2012\\
Contrato para analizar los efectos de una reducci\'on de muestreo sobre la distribuci\'on de tallas de especies blanco.

\textbf{Bi\'ologo, censo de focas de arpa,} Ministerios de Pesquer\'ias y Oc\'eanos, Canad\'a. 

\textbf{Dise\~{n}ador y desarrollador de bases de datos relacionales,} Ministerios de Pesquer\'ias y Oc\'eanos, Canad\'a.. 2007, 2008, 2009, 2011.

\textbf{Dise\~{n}ador y desarrollador de bases de datos relacionales,} Memorial University. 2007

\textbf{Miembro del Laboratorio de Mam\'iferos Marinos,} Centro Nacional Patag\'{o}nico (CENPAT), Argentina. 2001-2004
 
 \pagebreak
 
\section{EXPERIENCIA EN PROJECTOS DE INVESTIGACI\'ON}


{\bf Minimum realistic models of the Barents Sea and the Newfoundland and Labrador Shelf}. 2018-2020
\begin{itemize} % Use \item[] to prevent a bullet from appearing
	\item[] CoArc: A transatlantic innovation arena for sustainable development in the Arctic\\
	Principal Investigators: Dr Ulf Lindstr{\o}m, Dr Mariano Koen-Alonso
\end{itemize}

{\bf Ecophysiological responses of phocids to nutritional stress}. 2018-2020
\begin{itemize} % Use \item[] to prevent a bullet from appearing
	\item[] Fisheries and Oceans Canada and University of Pretoria (Southafrica)\\
	Investigators: Nico L\"ubcker, Dr. Alejandro Buren, Dr Nico de Bruyn, Dr Garry Stenson
\end{itemize}

{\bf Marine Mammal Expert Network}. 2017-2020
\begin{itemize} % Use \item[] to prevent a bullet from appearing
	\item[] Circumpolar Biodiversity Monitoring Program\\
	Conservation of Arctic Flora and Fauna\\
	Arctic Council
\end{itemize}

{\bf Natural Environment Research Council's Arctic Office (UK)}. 2018-2019
\begin{itemize}
	\item[] UK-Canada Bursaries Programme\\
	A Canary in a Cage: harp seals as indicators of climate change impacts in the Arctic\\
	Principal investigator: Dr James Grecian
\end{itemize}
{\bf Arctic Science Fund}. 2017-2019
\begin{itemize} % Use \item[] to prevent a bullet from appearing
	\item[] Fisheries and Oceans Canada\\
	Impacts of climate change on ringed seal growth and condition\\
	Principal Investigators: Dr Garry Stenson, Dr Alejandro Buren
\end{itemize}
{\bf Strategic Program for Ecosystem-Based Research and Advice}. 2017-2020
\begin{itemize} % Use \item[] to prevent a bullet from appearing
	\item[] Fisheries and Oceans Canada\\
	A predictive model of the environmental regulation of capelin\\
	Principal Investigators: Dr. Alejandro Buren, Dr. Paul Regular
\end{itemize}

\textbf{Fisheries Science and Ecosystem Research Program}. 2017-2019
\begin{itemize} % Use \item[] to prevent a bullet from appearing
	\item[] Fisheries and Oceans Canada\\
Principal Investigators: Dr. Pierre Pepin, Dr. Alejandro Buren; Dr. Mariano Koen-Alonso, Fran Mowbray, Dr. Paul Regular, Dr. Garry Stenson
\end{itemize}

\textbf{Natural Environment Research Council (UK)}. 2016-2018
\begin{itemize} % Use \item[] to prevent a bullet from appearing
	\item[] Can we detect changes in Arctic ecosystems?\\
Principal Investigators: Dr. C. Mahaffey, Dr. A. Tagliabue, Dr. R. Jeffreys, Prof. G. Wolff, Dr. A. Heath, Prof. R. Ganeshram, Dr. S. Smout, Dr. A. Yool, Dr. J. Hopkins, Dr. B. VanDongen, Dr. R. Stern \\
\url{https://arcticarise.wordpress.com/}
\end{itemize}

\textbf{Strategic Initiatives}. 2018-2019
\begin{itemize} % Use \item[] to prevent a bullet from appearing
	\item[] Fisheries and Oceans Canada\\
Follow up on variability in energy contents of key forage species in the NW Atlantic: evidence for changes in ocean productivity?
Principal Investigators: Dr. Garry Stenson, Dr. Alejandro Buren
\end{itemize}

\textbf{Center of Expertise in Marine Mammalogy}. 2017
\begin{itemize} % Use \item[] to prevent a bullet from appearing
	\item[] Fisheries and Oceans Canada\\
Implementation of automated software for detection and counting of harp and hooded seals \\
Principal Investigator: Dr. Garry Stenson
\end{itemize}

\textbf{Center of Expertise in Marine Mammalogy}. 2017
\begin{itemize} % Use \item[] to prevent a bullet from appearing
	\item[] Fisheries and Oceans Canada\\
New efforts to monitor marine mammal bycatch in Atlantic Canada\\
Principal Investigator: Dr. Jack Lawson
\end{itemize}

\textbf{Strategic Initiatives}. 2016-2017
\begin{itemize} % Use \item[] to prevent a bullet from appearing
	\item[]Fisheries and Oceans Canada\\
Variability in energy contents of key forage species in the NW Atlantic: evidence for changes in ocean productivity?\\
Principal Investigators: Dr. Garry Stenson, Dr. Alejandro Buren
\end{itemize}

\textbf{Strategic Program for Ecosystem-Based Research and Advice}. 2017-2018
\begin{itemize} % Use \item[] to prevent a bullet from appearing
	\item[]Fisheries and Oceans Canada\\
Influence of plankton and environment on biomass and condition of capelin\\
Principal Investigator: Dr. César Fuentes-Yaco
\end{itemize}

\textbf{Strategic Program for Ecosystem-Based Research and Advice}. 2016-2020
\begin{itemize} % Use \item[] to prevent a bullet from appearing
	\item[]Fisheries and Oceans Canada\\
Spatial and temporal overlap of cetacean habitat, cumulative noise, and protected areas in the Northwest Atlantic Ocean\\
Principal Investigator: Dr. Hillary Moors-Murphy
\end{itemize}

\textbf{Laurentian Channel Marine Protected Area Monitoring}. 2014-2015
\begin{itemize} % Use \item[] to prevent a bullet from appearing
	\item[]Fisheries and Oceans Canada\\
Principal Investigator: Dr. Jack Lawson
\end{itemize}

\textbf{Environmental Studies Research Fund}. 2013-2014
\begin{itemize} % Use \item[] to prevent a bullet from appearing
	\item[]Fisheries and Oceans Canada\\
Mid-Labrador marine megafauna and acoustic survey\\
Principal Investigator: Dr. Jack Lawson\\
\url{http://www.esrfunds.org/home}
\end{itemize}

\textbf{Ecosystem Research Initiative, ERI-NEREUS Program}. 2007-2012
\begin{itemize} % Use \item[] to prevent a bullet from appearing
	\item[]Fisheries and Oceans Canada\\
Ecosystem Research Initiative (ERI) for Newfoundland Region\\
Principal Investigator: Dr. Mariano Koen-Alonso\\
\url{http://www.dfo-mpo.gc.ca/science/publications/article/2014/03-31-14-eng.html}
\end{itemize}

\textbf{Species at Risk Program}. 2006-2008
\begin{itemize} % Use \item[] to prevent a bullet from appearing
	\item[] Fisheries and Oceans Canada\\
Estimating predation on Atlantic Cod by Seals off Newfoundland and in the northern Gulf of St. Lawrence \\
Principal Investigator: Dr. Garry Stenson
\end{itemize}



\textbf{International Polar Year}. 2007-2008
\begin{itemize} % Use \item[] to prevent a bullet from appearing
	\item[] Memorial University\\
How seabirds can help detect ecosystem change in the Arctic\\
Principal Investigator: Dr. William Montevecchi\\
\url{https://www.ec.gc.ca/api-ipy/default.asp?lang=En&n=7141EC8F-1}
\end{itemize}

\textbf{Natural Science And Engineering Research Council Strategic Project}. 2005-2007
\begin{itemize} % Use \item[] to prevent a bullet from appearing
	\item[] Memorial University\\
Importance of capelin (\textit{Mallotus villosus}) biology in sustaining trophic interactions in the Northwest Atlantic. \\
Principal Investigator: Dr. William Montevecchi.
\end{itemize}

\textbf{Agencia Nacional De Promoci\'{o}n Cient\'{i}fica y Tecnol\'{o}gica}. 2004-2006\\
(Argentinean National Agency for the Promotion of Science and Technology)
\begin{itemize} % Use \item[] to prevent a bullet from appearing
	\item[] University of Patagonia\\
Dynamics of the groups of dolphins affected by human activities and their inclusion in a marine protected areas management framework\\ 
Principal Investigator: Dr. Enrique Alberto Crespo
\end{itemize}

\textbf{Base line and monitoring study of marine mammals in National Park}. 2003-2004
\begin{itemize} % Use \item[] to prevent a bullet from appearing
	\item[] Marine Mammals Laboratory, CENPAT\\
Member of the Working Team of the Consultancy: Base line study and monitoring plan for marine mammals of the future National Park Monte Le\'{o}n\\
Principal Investigator: Dr. Enrique Alberto Crespo
\end{itemize}

\textbf{University of Patagonia}. 2002-2004
\begin{itemize} % Use \item[] to prevent a bullet from appearing
	\item[] Interactions between marine top predators and human activities in Patagonia\\
Principal Investigator: Dr. Enrique Alberto Crespo
\end{itemize}



\textbf{Agencia Nacional De Promoci\'{o}n Cient\'{i}fica y Tecnol\'{o}gica}. 2000-2002\\
(Argentinean National Agency for the Promotion of Science and Technology)
\begin{itemize} % Use \item[] to prevent a bullet from appearing
	\item[] University of Patagonia\\
Interactions between Fisheries and marine mammals in the Patagonian-Fueguinian coast\\
Principal Investigator: Dr. Enrique Alberto Crespo
\end{itemize}


\section{PUBLICACIONES EN REVISTAS CON REFERATO} 

%\begin{hangparas}{.4in}{1}
Diecisiete publicaciones en revistas con referato, cuatro publicaciones como primer autor. 

Publicaciones en las revistas: PLoS ONE; Marine Ecology Progress Series; Endangered Species Research; ICES Journal of Marine Sciences; Polar Biology; Canadian Journal of Zoology; Journal of Sea Research; Estuarine, Coastal and Shelf Science; Aquatic Biology; Science E-letters; Marine Biology; Journal of Northwest Atlantic Fishery Science; Latin American Journal of Aquatic Mammals.

\section{PRESENTACIONES EN CONFERENCIAS Y WORKSHOPS}


M\'as de cincuenta presentaciones orales en conferencias, workshops y como orador invitado. Cinco presentaciones de p\'osters en conferencias.

Algunas conferencias relevantes: ICES Annual Science Conference,  International Marine Conservation Congress, Biennial Conference on the Biology of Marine Mammals, American Fisheries Society Annual Meeting, Arctic Frontiers, International Congress for Conservation Biology, NAMMCO SC Working Group on Marine Mammals and Fisheries Interactions ICES/NAFO/NAMMCO Symposium on the Role of Marine Mammals in the Ecosystem in the 21$^{st}$ Century, Pacific Seabird Group Conference.



\section{PREMIOS Y BECAS}
Doce premios y becas recibidas, por excelencia en el desarollo de actividades acad\'emicas. 

Entes emisores: Organizaci\'on de los Estados Americanos, Memorial University, University of British Columbia, Society for Marine Mammalogy, Universidad Nacional de la Patagonia San Juan Bosco, Ministerio de Educaci\'on de la Provincia del Chubut.



\section{REVISOR DE REVISTAS CON REFERATO}

Ecology, Canadian Journal of Fisheries and Aquatic Sciences, Global Change Biology, Proceedings of the Royal Society B, Journal of Applied Ecology, Marine Ecology Progress Series, ICES Journal of Marine Sciences, Journal of Avian Biology, Waterbirds


\end{resume}

\end{document}
